%%Conclusion

In our paper, we did ethical analysis on the question ``Is censorship ethical to be applied for regulation of violent online games?" using Kantian and utilitarianism theories for both opposing and supporting censorship, respectively. Since more and more experiments and data show correlations between aggressive behaviors of children and media violence, especially violent online games, it is necessary for everyone to be aware of what is happening now. According to our analysis, Kantian theories prove that censorship is unethical because it violates both 1st and 2nd formulations. It also undermines the freedom of speech which would stifle the creation and imagination of designers. However, from another point of view, utilitarianism indicates the necessity of censorship since the benefits and positive impacts for all of the stakeholders far outweigh the costs or negative impacts. Based on the existing solutions, we presented some possible solutions for this ethical issue, in law, market, social norms and code parts, aiming to find a compromise when considering the interests of stakeholders.

In future work, there should still be a focus on the improvement of solutions since internet and digital media technologies are changing very fast so that it keeps creating policy vacuums for regulations. Our proposed solutions are based on our analysis and theory, and may face some difficulties during implementation. It is necessary to consider the feasibility and effectiveness of them according to the actual situation of our society. Despite that ethical issues involving in the digital media technologies and internet are always open topics, they are coming to be highly emphasized and must be considered comprehensively. In conclusion, no matter how our world will be changed by technologies, it requires everyone to have this consciousness of self-protection, objectivity, and reality.